%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {B.E in Computer Engineering} % Degree
    {Sanjivani College of Engineering (Savitribai Phule Pune University)} % Institution
    {Kopargaon, Maharashtra} % Location
    {Aug. 2012 - June. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      	\item {Project \textbf{Smart Farm Using Wireless Sensors Network} awarded as \textbf{Best project of the year 2016}.}
        \item {Published research paper on project \textbf{Smart Farm Using Wireless Sensors Networks} in IJCA Journal.}  
        \item {Runner-up in \textbf{WEB-WRANGLE} Web Designing and Programming contest.}
        \item {Best performer in \textbf{Summer Training \& Internship Program - 2014}, organized by \textbf{Network Bulls, Delhi}.}
        \item {Guided team of 10 juniors for Live Project \textbf{Campus Connect} sponsored \textbf{Techathon Networks}.}
        \item {Attended training and hands-on for \textbf{Cloud Computing}, conducted by Technophilia Systems.}      
		\item {Technical presentation on \textbf{SNORT - Network Intrusion Detection \& Prevention System}.}         
      \end{cvitems}
    }
    \cventry
    {Diploma in Computer Technology} % Degree
    {Sanjivani's K. B. P Polytechnic College (Mumbai University)} % Institution
    {Kopargaon, Maharashtra} % Location
    {May. 2009 - June. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      	\item {Project \textbf{Departmental Online Examination} awarded as \textbf{Best project of the year 2012}.}
        \item {Vice-president of \textbf{Association of Computer Technology Students} for academic year 2012-2012.}
        \item{Organized various events such as Programming Contests, Code Debugging Contest etc. for students.}         
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
