%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Senior Backend Engineer (Remote)} % Job title
    {ColorElephant LDA} % Organization
    {Remote} % Location
    {April. 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Helping large scaled multi-million dollar e-commerce company developing critical business services.}
        \item {Worked on custom integration of multiple payment methods like \textbf{ApplePay, AmazonPay, PayuOS, Sella, BitPay, PayPal, Stripe} (3DS and SCA complied) for 30+ countries with multiple application, extensively in Laravel and Vue.}
        \item {Occasionally represent ColorElephant and speak at local Laravel meetups in Mumbai and Pune on tools and workflows using in ongoing projects.}
        \item {Worked on developing large scale systems with high architectural and design considerations.}
        \item {Designed frontend agnostic base application and private packages with Laravel, implementing features which are repeated in multiple projects which are leveraged using APIs by mobile apps and frontend apps.}
        \item {Worked on designing one of the complex multi type API integration in single application, working as middleware and leveraged by 3rd party vendors using SOAP, FTP, XML, REST APIs.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Senior Product Engineer (Part of Business Strategy \& Innovations)} % Job title
    {MYVIZO} % Organization
    {Thane, Maharashtra - India} % Location
    {Jun. 2016 - March 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Reporting directly to co-founders.}
        \item {Designed and developed an flagship product from scratch called \textbf{Automated Video Interviews (AVI)} for B2B business clients, which used for campus recruitment and lateral hiring.}
        \item {Designed and developed an product from scratch called, \textbf{ Live Interviews} for B2B business clients, featuring multi user multi location with scorecard, text chat and realtime file sharing .}
        \item {Implemented \textbf{RESTful API} for MYVIZO Internal Application which was built with Ionic 2 for official use.}
        \item {Implemented \textbf{high-availability} API for candidate interviewing Android and IOS applications.}
        \item {Built and deployed overall services using \textbf{Nginx, Apache, Shippable}, and several AWS stack(\textbf{Including EC2, Elastic Beanstalk, Route 53, S3, CloudFront, RDS, Cognito, IAM, Certificate Manager}), focusing on high-availability, fault tolerance, and auto-scaling.}
        \item {Implemented \textbf{OAuth2 Server} to authenticate internal official services using single sign-on and to integrate with Amazon Alexa Skills.}
        \item {Automated daily tasks with \textbf{Amazon Alexa} to provide instant statistics, reports and make emergency backups.}
        \item {As a best practice, followed \textbf{Test Driven Development} approach in feature development.}
        \item {Extensively used \textbf{Gitlab} for project repository, daily code reviews, CI/CD using gitlab runners, issue boards, service desk to handle user support requests etc. }
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
