%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Build natural voice experience with Laravel Application \& Amazon Alexa} % Affiliation/role
    {LaravelLive - 2018 Speaker (Laravel India Conference)} % Organization/group
    {New Delhi, laravellive.in} % Location
    {17 March, 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {LaravelLive's goal is to bring together bright minds to give talks that are idea-focused, and on a wide range of subjects in PHP Laravel, to foster learning, inspiration and provoke conversations that matter.}
        \item {LaravelLive brings top notch developers of the ecosystem together, to inspire new talent around the country to learn and contribute to the open source.}
        \item {I will be speaking on, \textbf{Secure Integration of Laravel Application and Amazon Alexa to automate daily tasks} along with 5 more inspiring speakers in this 1 day event.}
        \item {Designed \textbf{LaravelLive - 2018} event website(\href{http://laravellive.in}{http://laravellive.in}) using \textbf{Laravel 5.5 and TailwindCSS}.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Open source - Package Maintainer, Active Contributor} % Affiliation/role
    {Vue Dropzone} % Organization/group
    {@rowanwins/vue-dropzone} % Location
    {Author - Rowan Winsemius} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {A Vue.js component for Dropzone.js - a drag’n’drop file uploads utility with image previews.}
        \item {Redesigned complete component to support Vue2 with Author.}
        \item {Contributed additional feature \textbf{Direct upload to AWS S3 from browser using pre-signed url}, which is not available with core package of dropzone.js.}
        \item {Focusing on bug fixing, resolving user queries on github, review PRs, improving documentation and publishing \& maintaining updated versions on npm.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Open source - Author} % Affiliation/role
    {Vue Circle Progress} % Organization/group
    {@vrajroham/vue-circle-progress} % Location
    {Author - Self} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item{A Vue.js component to draw \textbf{animated circular progress bars}.}
        \item{Wrapper is designed around the jQuery library to effectively use with SPA in one of the product dashboard at MYVIZO.}
        \item {Focusing on bug fixing, resolving user queries on github, review PRs, publishing and maintaining updated versions on npm.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Open source - Author} % Affiliation/role
    {Vue Simple Lightbox} % Organization/group
    {@vrajroham/vue-simple-lightbox} % Location
    {Author - Self} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {A Vue.js component for \textbf{touch-friendly image lightbox for mobile and desktop} with simple-lightbox.}
        \item {Wrapper is designed around the simple-lightbox core javascript package, which exposes underlying core API for customization.}
        \item {Focusing on bug fixing, resolving user queries on github, review PRs, publishing and maintaining updated versions on npm.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
