%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {MYVIZO} % Affiliation/role
    {Ondemand Video Interviews and Live Interviews} % Organization/group
    {myvizo.com} % Location
    { } % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {The product enables hirers to Judge Personality, Competence and Culture of a pool of candidates without hassle of coordination and personal time allocation. It helps in prioritizing and picking best fit candidates.}
        \item {This tool allows hirers to step back and relax, when a pool of candidates is simultaneously giving answers to certain preset questions for an opening.}
        item {Responsible for complete \textbf{Architecture and Technology Stack} implementation, followed TDD approach for development.}
        \item {Product technical stack consist \textbf{Laravel, Vue.js, WebRTC and RecordRTC, Node.js} for implementation, hosted in AWS Auto-scaling, fault tolerant, high availability, secure on multi-region environment.}
        \item {Implemented compression and transcoding algorithm to compress high volume of videos using \textbf{FFMPEG and AVCONV}, without compromising video quality and availability.}
        \item {Implemented \textbf{Live Interviews} module which enables multiple HR users to have a face to face interview with inbuilt score-pad, live chat and realtime file sharing features}
        \item {Above implementation completely utilizes \textbf{WebRTC} feature of modern browsers, and importantly WITHOUT using Flash support.}
        \item {Implemented API's for Android and IOS applications for same product.}
        \item {Involved in daily code reviews setting DevOps tasks like CI/CD using \textbf{Gitlab Runners and Shippable} for automated deployment.}
        \item {Developed \textbf{Amazon Alexa Skills} to provide voice powered features to on-boarded corporates and integrated developed skills securely with existing product using \textbf{OAuth2 Server}. }
        \\
      \end{cvitems}
    }
   %---------------------------------------------------------
    \cventry
    {MYVIZO} % Affiliation/role
    {Internal Operationl Process Automation and ATS} % Organization/group
    {myvizo.com} % Location
    { } % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Automated organizations internal operational process with various features like employee management, position management, payment tracker etc.}
        \item {Product technical stack consist \textbf{Laravel, Vue.js} for implementation and hosted on AWS EC2 instance.}
        \item {Implemented API's for internal application built using Ionic2.}
        \item {Developed \textbf{Amazon Alexa Skills} to provide voice powered features to co-founders and administrators to automate daily task, such as taking backup, daily summary/statistics, listening fullstack radio etc. }
        \item {Implemented \textbf{Applicant Tracking System (ATS)} to track and maintain candidate records  seamlessly who have ever applied for any position on site or involved in any recruitment process.}
        \\
      \end{cvitems}
    }
   %---------------------------------------------------------
    \cventry
    {Sanjivani College of Engineering} % Affiliation/role
    {Smart Farm Using Wireless Sensors Network} % Organization/group
    {Computer Engineering} % Location
    { } % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Being from farmers family I was knowing and undergone the hurtles which costs more and can be minimized by technology solution, so tried to implement this innovative concept.}
        \item {Project model helps farmers to monitor their polyhouse/greenhouse temperature, CO2 level and humidity.}
        \item {Architecture consists of \textbf{ZIGBEE Network Topology, Lightweight Pythong server running on BeagleBone Black and batteries}}
        \item {Implemented \textbf{fault tolerant, multipath mesh network topology} of xbee devices mounted with various sensor modules and continuously transmitting data to coordinator XBEE node.}
        \item {Continuous transmitted data is dumped in live database by light weight server which is served realtime to farmer on his mobile application. }
        \item{Mobile application is developed in \textbf{Ionic framework in native/regional language}, from application remote devices/sensors like fans, air flow curtains can be controlled.}
        \item {From precise location of farm, exact weather conditions are displayed to farmers which are fetched from weather.com realtime.}
        \item {Presented and published research paper in \textbf{International Conference} as mentioned in publications section, later applied for patent.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
